### 2025-07-12 multiple-regression.qmd
20250711 - exponentiate regression coefficients

where $p$ is the number of [predictor variables](#sec-correlationalStudy).
Multiple regression is basically a weighted sum of the [predictor variables](#sec-correlationalStudy), and adding an intercept.
Under the hood, multiple regression seeks to identify the best weight for each [predictor](#sec-correlationalStudy).

@@

summary(logisticRegression)
performance::r2(logisticRegression)
print(effectsize::standardize_parameters(logisticRegression, method = "refit"), digits = 2)
```

@@

summary(ordinalRegression)
performance::r2(ordinalRegression)
print(effectsize::standardize_parameters(ordinalRegression, method = "refit"), digits = 2)
```

@@

summary(poissonRegression)
performance::r2(poissonRegression)
print(effectsize::standardize_parameters(poissonRegression, method = "refit"), digits = 2)
```

@@

summary(negativeBinomialRegression)
performance::r2(negativeBinomialRegression)
print(effectsize::standardize_parameters(negativeBinomialRegression, method = "refit"), digits = 2)
```

>>>>

where $p$ is the number of [predictor variables](#sec-correlationalStudy).
Multiple regression is basically a weighted sum of the [predictor variables](#sec-correlationalStudy), and adding an intercept.
Under the hood, multiple regression seeks to identify the best weight for each [predictor](#sec-correlationalStudy).
The intercept is the expected value of the outcome variable when all of the predictor variables have a value of zero.

@@

summary(logisticRegression)
performance::r2(logisticRegression)
print(effectsize::standardize_parameters(logisticRegression, method = "refit"), digits = 2)

broom::tidy(
  logisticRegression,
  exponentiate = TRUE,
  conf.int = TRUE)
```

@@

summary(ordinalRegression)
performance::r2(ordinalRegression)
print(effectsize::standardize_parameters(ordinalRegression, method = "refit"), digits = 2)

broom::tidy(
  ordinalRegression,
  exponentiate = TRUE,
  conf.int = TRUE)
```

@@

summary(poissonRegression)
performance::r2(poissonRegression)
print(effectsize::standardize_parameters(poissonRegression, method = "refit"), digits = 2)

broom::tidy(
  poissonRegression,
  exponentiate = TRUE,
  conf.int = TRUE)
```

@@

summary(negativeBinomialRegression)
performance::r2(negativeBinomialRegression)
print(effectsize::standardize_parameters(negativeBinomialRegression, method = "refit"), digits = 2)

broom::tidy(
  negativeBinomialRegression,
  exponentiate = TRUE,
  conf.int = TRUE)
```
